Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Add description of results in 5.5

Our experiments span 13 pairs of cooperative kernels and data sets, 3
classes of non-cooperative kernel workloads and frequency, 4 quantities
of workgroups claimed for the non-cooperative kernel and 2 variations of
resizing barriers for graph algorithms, leading to 288
configurations. Each of this configuration is run 10 times on each
GPU. For each run, we record the execution time of the cooperative
kernel. For each scheduling of the non-cooperative kernel during the
run, we also record the \emph{gather time} needed by the scheduler to
collect enough workgroups to launch the non-cooperative kernel, and the
non-cooperative kernel execution time. We make sure all kernels perform
their computations by comparing their result with expected results. We
had to ignore some configurations where the non-cooperative kernel asks
for all but one workgroups (namely bc, bfs and l-sssp on all chips, and
color on Iris), and the game application on HD520, since they lead to
system issues like GPU deadlock or blue screens---which we think are
manifestations of driver bugs.

@@

\paragraph{Results}  \ADComment{Discuss the results.}
explain horizontal lines

missing results for all but one in bfs rmat22 since errors

also, high gather time corresponds to applications and data sets where
resize/kill is triggered less often.

Each configuration was run 10 times on each GPU.

@@

>>>>

Our experiments span 13 pairs of cooperative kernels and data sets, 3
classes of non-cooperative kernel workloads and frequency, 4 quantities
of workgroups claimed for the non-cooperative kernel and 2 variations of
resizing barriers for graph algorithms, leading to 288
configurations. Each of this configuration is run 10 times on each
GPU. For each run, we record the execution time of the cooperative
kernel. For each scheduling of the non-cooperative kernel during the
run, we also record the \emph{gather time} needed by the scheduler to
collect enough workgroups to launch the non-cooperative kernel, and the
non-cooperative kernel execution time. We make sure all kernels perform
their computations by comparing their result with expected results. We
had to ignore some configurations where the non-cooperative kernel asks
for all but one workgroups (namely bc, bfs and l-sssp on all chips, and
color on Iris), and the game application on HD520, since they lead to
system issues like GPU deadlock or blue screens---which we tend to think
are manifestations of driver bugs.

@@

\paragraph{Results}  \ADComment{Discuss the results.}

\myfig~\ref{fig:fine-grained-timing} reports the measure for three
configurations and represents the gather and execution time of the
non-cooperative kernel w.r.t. the quantity of workgroups allocated to
it. Times are in milliseconds, and a logarithmic scale is used since
gather times tend to be much smaller than execution times. The
horizontal grey lines indicates the desired rate for non-cooperative
kernels.

Responsiveness of the cooperative scheduling is measured by the gather
time. In all examples, we observe that the gather time grows as we ask
for more workgroups for the non-cooperative kernel: this is expected,
since the scheduler must wait for more workgroups to call $\offerkill$
or to reach a resizing barrier. Still, notice that the query barrier
leads to better and stable gather times for graph applications, since it
can collect all needed workgroups at the first time they pass through
the barrier. Gather time also application-dependent since it is related
to how often the cooperative kernel workgroups hit $\offerkill$ or
$\resizingglobalbarrier$.

\HEComment{missing results for all but one in bfs, discussed in expe
setup, do we need to say it here ?}

@@

\HEComment{Figure gather time: replace ``O'' by ``M'' , ie max nb of active workgroups}

\HEComment{Figure gather time: add ``ms'' to time coordinate}

\HEComment{Figure gather time: lower legend in hd5500 bfs figure}

\HEComment{Figure gather time: use consistent line styles for work stealing (ie, same style for ``heavy'' across all figures)}
